%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol} % header is two column
\usepackage{calc}
\usepackage{hyperref}

% spacing is 125% font size is 12 for readability
\fontsize{12}{16}\selectfont%

\addbibresource{publications.bib}

% setup footer
\lfoot{%
	\makebox[0.20\textwidth][l]{\textbf{Legault, Jean-Philippe}}% left side
	\makebox[0.60\textwidth][c]{\footnotesize Generated \href{https://github.com/jeanlego/CV/releases}{github.com/jeanlego/CV} on \today}% center
	\makebox[0.20\textwidth][r]{\thepage~of~\pageref{LastPage}}% right side
	}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%   TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

{ \topskip0pt \parskip0pt \setlength{\columnsep}{24pt}

\begin{multicols}{2}

	\vspace*{\fill}
	\raggedleft

	\colorbox{white}{{\HUGE\textcolor{black}{{\MakeUppercase{Jean-Philippe}}}}}

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Legault}}}}}

	{\huge%
		Researcher\\[2pt]
		Software Developer}

	\columnbreak

	\vspace*{\fill}

	{%
		\raggedright
		\tt

		% minor fix for map icon
		\hspace*{1pt}\icon{MapMarker}{12}{\hspace*{2pt}Palo Alto, CA, US, 94306}
		\vspace*{5pt}

		\icon{Phone}{12}{on request}
		\vspace*{5pt}

		\icon{At}{12}{\href{mailto:jeanphilippe.legault@unb.ca}{jeanphilippe.legault \[at\] unb \[dot\] ca}}
		\vspace*{5pt}

		\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/jean-philippe-legault-1489ab173}{jean-philippe-legault-1489ab173}}
		\vspace*{5pt}

		\icon{Github}{12}{\href{https://github.com/jeanlego}{jeanlego}}

	}

\end{multicols}
\vspace*{-\baselineskip}

{\color{linecolor}
	%%%%%%%%%% params
	\newlength{\lineWidth}
	\setlength{\lineWidth}{0.5\textwidth}
	\newlength{\topLen}
	\setlength{\topLen}{.12\textwidth}
	\newlength{\bottomLen}
	\setlength{\bottomLen}{.155\textwidth}

	%%%%%%%%%% create the lines
	\hspace*{\fill}\rule{\lineWidth}{.4pt}\hspace*{\fill}

	\vspace*{-\topLen}
	\hspace*{\fill}\rule{.4pt}{\topLen+\bottomLen}\hspace*{\fill}
	\vspace*{-\bottomLen}
}

\vspace*{-\baselineskip}
\begin{multicols}{2}

	\RTLpar\sloppy

	During my master's in Computer Science, I have gained expertise in language runtimes and FPGA development.
	My broad interests allow me to use lateral thinking to solve complex problems.
	I can efficiently visualize problems, design solutions, and communicate abstract ideas, allowing me to be an effective team member.
	My experience in academia, working two years as a senior, and as a lead developer, has shaped me into an effective leader.
	Working on both commercial and open-source projects has made me adaptable to new workflows.

	\vspace*{\fill}
	\columnbreak

	\justifying \sloppy

	\cvsect{Languages}

	\vspace*{-4pt}
	\bulletedlist{
		French---\texttt{native},
		English---\texttt{fluent}
	}

	\vspace*{5pt}

	\ifdefined\academicCV {%
		\cvsect{Research Interest}
	} \else {%
		\cvsect{Interest}
	} \fi

	\vspace*{-4pt}
	\bulletedlist{
		Software and Computer Engineering:\\Compilers,
		Distributed Computing,
		Embedded Systems,
		FPGA,
		High-Level Synthesis,
		Operating Systems,
		Virtual Machines
	}
	\vspace*{5pt}

	\cvsect{Programming Languages}

	\vspace*{-4pt}
	\bulletedlist{
		ArmV8,
		Bash,
		Blif,
		C++,
		C,
		Java,
		LaTex,
		Perl,
		Python,
		Verilog,
		VHDL
	}

	\vspace*{\fill}
\end{multicols}
}

% reset settings
\justifying

% footnote

\cvsect{Education}

\entrys
{2018 -- 2020}
{Master in Computer Science}
{University of New Brunswick | NB, Canada}
{JIT Compilers, Embedded System Software Development and FPGA CAD:
	\begin{tightemize}
		\item FPGA CAD tool (CS6999)
		\begin{smallQuote}
			Project-based: Redesign sequential logic synthesis to support multiple clock domain and multiple edge sensitivity in Odin II.
		\end{smallQuote}

		\item Operating Systems (CS6605)
		\begin{smallQuote}
			A comprehensive study of computer operating systems: process synchronization, concurrency, multi-processor systems, virtual memory, advanced file systems, distributed systems.
			Design a i386 multi-tasking Kernel.
		\end{smallQuote}

		\item Machine Learning \& Data Mining (CS6735)
		\begin{smallQuote}
			Cover: inductive inference of decision trees, neural network learning, generic algorithms, Bayesian methods, Information-Theoretic classification, and reinforcement learning.
			Focus on theoretical concepts of machine learning such as inductive bias, Occam's razor, models of noise, uniform convergence, and Fourier analysis methods.
		\end{smallQuote}

		\item Dynamic Memory Management (CS6905)
		\begin{smallQuote}
			Study a statically typed functional language and use it to write interpreters and demonstrating these core concepts.
			Learn the main techniques of memory management including allocation, liveness detection, reference counting, and generational collectors.
		\end{smallQuote}
	\end{tightemize}
}

\entrys
{2019}
{Diploma in University teaching}
{University of New Brunswick | NB, Canada}
{}

\entrys
{2015 -- 2017}
{Bachelor's in Computer Science with Honours}
{University of New Brunswick | NB, Canada}
{Honours in FPGA Architecture Design:
	\begin{tightemize}
		\item Natural Language Processing (CS4765)
		\begin{smallQuote}
			Topics include fundamental topics in natural language processing such as n-gram language models, part-of-speech tagging, parsing, lexical semantics, spelling correction, document classification.
			Implement and evaluate a variety of natural language processing methods and their performance.
		\end{smallQuote}

		\item Intro to Parallel Processing (CS4745)
		\begin{smallQuote}
			Parallel computer architectures, design and analysis of parallel algorithms, parallel programming languages, case studies, selected numerical and non-numerical applications.
		\end{smallQuote}

		\item Intro to Artificial Intelligence (CS4725)
		\begin{smallQuote}
			Introduction to intelligent agent design, problem-solving using search techniques, the use of mathematical logic for knowledge representation and reasoning, decision making under uncertainty.
		\end{smallQuote}

		\item Digital Logic Design (ECE2214)
		\begin{smallQuote}
			This is an introductory course to practical aspects of digital systems design. The course includes the design of digital circuits with CAD tools and VHDL hardware description language.
		\end{smallQuote}
	\end{tightemize}
}

\entrys
{2012 -- 2014}
{Aerospace Engineering Technician}
{École Nationale d'Aérotechnique | QC, Canada}
{Completed 56 credit towards a College diploma:
	\begin{smallQuote}
		Conceive and fabricate aeronautical parts using Computer-Aided Design (CAD) tool---Catia V5;\\
		Plan the fabrication step and assembly of the airframe, engines, and other aeronautical components;\\
		Fabricate elements of the airframe using composite materials and sheet metal;\\
		Plan of the production, quality assurance and testing process of aerospace components.
	\end{smallQuote}
}

\cvsect{Awards \& Grants}

\entrys
{2020}
{Research Grant}
{Google}
{30,000\$USD for one year towards a reusable Odin II Partial Mapper.\footnotemark}

\footnotetext{\fullcite{google}}

\entrys
{2015 -- 2016}
{Dean's List}
{University of New Brunswick | NB, Canada}
{Awarded to students who maintained a GPA above 3.7 throughout the academic year}

\cvsect{Scholarships}

\entrys
{2018 -- 2020}
{Research Fellowship}
{University of New Brunswick | NB, Canada}
{23,500\$/yr. research fellowship  with the Centre for Advanced Studies---Atlantic on the Eclipse OMR project}

\entrys
{2015 -- 2016}
{Sir George E. Foster}
{University of New Brunswick | NB, Canada}
{2000\$/yr. Awarded to students who maintained a GPA above 3.7 throughout the academic year.}

\cvsect{Experience}

\entrys
{Apr. 2021 -- cur.}
{Senior Software Developer}
{Rivian | Canada}{
	\textbf{\href{https://rivian.com/}{rivian.com}}\\
	Create services and middleware for Rivian’s in-vehicle infotainment system which links drivers and passengers to their vehicle and the outside world.
	\begin{tightemize}
		\item Collaborate with Platform Software, HMI developers, System Design, and Test Engineers to realize a modern in-vehicle experience
		\item Test the in-vehicle experience in the lab and in Rivian prototype vehicles.
		\item Troubleshoot and resolve issues found during testing
		\item Help drive research into new technologies and interfaces.
		\item Collaborate with other divisions in understanding and sharing of technology roadmaps, portfolios and intellectual property.
		\item Work with extensively Android AOSP and QNX Hypervisor at the platform and service level.
		\item Create a holistic Logging solution for different ECU's, help improve in-house IPC solutions.
	\end{tightemize}

}


\entrys
{Nov. 2020 -- Apr. 2021}
{Software Developer}
{Meson Labs Ltd. | Canada}{
	\textbf{\href{https://www.mesonlabs.ca/}{mesonlabs.ca}}\\
	Improve a secure Pre-Boot Authentication image to chainload signed kernels and accessorize OPAL SED tools for PBA image using Bash.
	\begin{tightemize}
		\item Use Buildroot extensively to create embedded images.
		\item FPM to package applications.
		\item Built a framework to automate binaries/files installation/update/downgrade into an image using FPM and Makefiles.
		\item Review other developers' code.
		\item Patch drivers for Windows and Linux.
	\end{tightemize}
}

\entrys
{2019 -- 2020}
{Lead Developer}
{Centre for Advance Studies Atlantic | NB, Canada}{
	Maintain the Synthesis tool of the Verilog to Routing Project, Odin II and manage the Odin II project.
	\begin{tightemize}
		\item Organize meetings (quarterly, weekly and daily scrum)
		\item Take part in steering committee meetings for the project.
		\item Architect design changes and new features for developers to implement
		\item Mentor new developers and carve a roadmap for them.
		\item Manage other developers and review their merge requests.
		\item Fix Bugs and broken features.
		\item Build new features and improve compliance with the synthesizable subset of IEEE-1364-2005 (Verilog 2005)
		\item Improve the tool usability and documentation for both developers and users.
		\item Improve the regression suite to catch bugs and regression in features.
	\end{tightemize}
}

\entrys
{
	Contracts\\
	\begin{tightemize}
		\item[] {\footnotesize SM-2019}
	\end{tightemize}
}
{Instructor}
{University of New Brunswick | NB, Canada}
{
	\begin{tightemize}
		\item CS2263---Systems Software Development
		\begin{smallQuote}
			Procedural program development and supporting tools, using the C language.
			Topics include implementation of data structures, memory management, compilation/linking, building, debugging, and version control.
		\end{smallQuote}
	\end{tightemize}

}

\entrys
{2019 \\{\footnotesize Feature contract}}
{Software Developer, Multithreading \& C ++ Expert}
{Butterfly Energy Systems | NB, Canada}
{
	\textbf{\href{http://www.butterflyenergy.ca/home.php}{butterflyenergy.ca}}\\
	Responsible to track down a null pointer exception in a multithreaded C++ OOP codebase.
	It was traced back to a race condition because of an uncaught spurious wake of a thread; A class was deleted during the execution of one of its method.
}

\entrys
{
	Contracts\\
	\begin{tightemize}
		\timestamp{WI-2018}
		\timestamp{SM-2018}
		\timestamp{FA-2018}
	\end{tightemize}
}
{Teaching Assistant}
{University of New Brunswick | NB, Canada}
{
	\begin{tightemize}
		\item Computability and Formal Languages
		\item Professional Practices
		\item Professional Practices
	\end{tightemize}
}

\entrys
{
	Contracts\\
	\begin{tightemize}
		\item[] {\footnotesize FA-2018}
	\end{tightemize}
}
{Tutor}
{University of New Brunswick | NB, Canada}
{
	\begin{tightemize}
		\item Operating Systems I (CS3413) Rachelle Potter
	\end{tightemize}
}

\entrys
{2015 -- 2018}
{Electronic and Software Technician}
{Canada Electronic Parts Online Inc. | NB, Canada}{
	Repairing electronic devices, i.e. smartphones, televisions, computers.
	\begin{tightemize}
		\item Played a significant role in increasing sales and revenue by increasing outreach.
		\item Broadened the company's expertise in electronic repairs and introduced tooling and techniques to repair devices with surface mount components.
		\item Increased repairs success rate and revenue.
		\item Introduced software-based repairs and debugging (i.e. reflashing lost IMEI or CMOS)
		\item Introduced corrupted or defective hard drive data recovery.
	\end{tightemize}
}

\cvsect{Project Contributions}

\entrys
{2018 -- 2020}
{Eclipse OMR}
{\href{https://github.com/eclipse/omr}{github://eclipse/omr}}{
	Responsible for initiating the work on the basic implementation of an ARM64V8 specific OMR; This involved making the full suite of hardware operation in the ARM64V8 documentation (or AArch64) available to the JIT compiler.
	Weekly meetings were held on infrastructure design and implementation.
	The project was lead by the IBM Runtimes Team in Ottawa, and work was done conjointly with members of the IBM Japan team.
}

\entrys
{2017 -- 2020}
{Odin II}
{\href{https://github.com/verilog-to-routing/vtr-verilog-to-routing/graphs/contributors}{github://verilog-to-routing}}{
	Maintain the Front-End Verilog Synthesis tool of the Verilog to Routing Project.
	\begin{tightemize}
		\item Managing other developers and review their merge requests.
		\item Fix Bugs and broken features.
		\item Build new features and improve the tool usability and documentation for both developers and users.
	\end{tightemize}
}

\cvsect{Data Interchange Formats}

\bulletedlist{
	JSON,
	XML,
	TOML,
	YAML
}

\vspace*{\baselineskip}
\cvsect{Tools}

\bulletedlist{
	Make,
	CMake,
	Bison,
	Flex,
	Bash,
	Buildroot,
	Git,
	Jenkins,
	Docker,
	KVM,
	Cross-Compilers,
	Quartus,
	Verilog-To-Routing,
	GDB,
	Valgrind,
	AutoCAD,
	FreeCAD,
	Office Suite,
	CatiaV5
}

\vspace*{\baselineskip}
\cvsect{Operating Systems}

\bulletedlist{
	Linux,
	BSD,
	OSx,
	Windows
}

\vspace*{\baselineskip}
\cvsect{Other Knowledge}

\bulletedlist{
	Networking,
	Linux Development,
	Drafting,
	Sheet Metal Work,
	Welding,
	Electronic,
	Embedded System Development,
	CAD Drawing
}

\vspace*{\baselineskip}
\cvsect{Interest}

\bulletedlist{
	Electronics,
	Networking,
	Programming,
	Fabrication,
	Machining,
	Wood Working,
	Automation,
	Backcountry Camping,
	Hiking
}
\vspace*{\baselineskip}

\ifdefined\academicCV {%

	\cvsect{Travel Grant}

	\tightentry{2020}{International Symposium on FPGA}{Monterey, California, United-States}
	\tightentry{2019}{Cascon}{Markham, Ontario, Canada}
	\tightentry{2018}{Cascon}{Markham, Ontario, Canada}
	\tightentry{2018}{Castle}{Markham, Ontario, Canada}
	\tightentry{2018}{Splash}{Boston, Massachusetts, Canada}
	\tightentry{2018}{CMC Microsystem TEXPO}{Toronto, Ontario, Canada}

	\vspace*{\baselineskip}
	\cvsect{Mentoring {\footnotesize(Unofficial Supervision)}}

	\tightentry{2020 -- cur.}{Daniel Stokes}{Honours, B.CS., University of Waikato, New Zealand}
	\tightentry{2020 -- cur.}{Eve MacDonald}{Work Term, B.EE, University of New Brunswick, Canada}
	\tightentry{2020}{Shrey Vyas}{Work Term, M.CS, University of New Brunswick, Canada}
	\tightentry{2019 -- 2020}{Mohammad Sohrabi}{Ph.D. CS, University of New Brunswick, Canada}
	\tightentry{2019 -- cur.}{Seyed Alireza Damghani}{M.  CS, University of New Brunswick, Canada}
	\tightentry{2019}{Michael Flawn}{Honours, B.CS., University of New Brunswick, Canada}
	\tightentry{2019}{Alexandrea Demmings}{Work Term, B.SwE, University of New Brunswick, Canada}
	\tightentry{2019}{Julie Brown}{Work Term, B.CEE, University of New Brunswick, Canada}
	\tightentry{2018}{Nasrin Eshraghi Ivari}{Ph.D. CS University of New Brunswick, Canada}

} \fi

\ifdefined\academicCV {%

	\nocite{*}
	\blfootnote{Presentors are \underline{underlined}}

	\defbibheading{pip}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{In Proceeding Papers}\vspace*{-6pt}}
	\printbibliography[heading=pip, keyword=inprogresspapers]

	\defbibheading{pubp}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Published Papers}\vspace*{-6pt}}
	\printbibliography[heading=pubp, keyword=publishedpapers]

	\defbibheading{diss}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Dissertations}\vspace*{-6pt}}
	\printbibliography[heading=diss, keyword=dissertations]

	\defbibheading{talks}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Talks}\vspace*{-6pt}}
	\printbibliography[heading=talks, keyword=talks]

	\defbibheading{poster}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Conference Posters}\vspace*{-6pt}}
	\printbibliography[heading=poster, keyword=poster]

	\vspace*{-6pt}
	\vspace*{\baselineskip}

} \fi

\cvsect{Academic References}

\entrys%
{Dr. Kenneth B. Kent}{Thesis Supervisor}
{University of New Brunswick | Fredericton, New Brunswick, Canada}
{\texttt{ON REQUEST}

	Supervised me during my master's thesis and is the code owner of the Odin II project.
}

\entrys%
{Dr. Panos Patros}{Mentor and External Collaborator}
{University of Waikato | Hamilton, Waikato, New Zealand}
{\texttt{ON REQUEST}

	Working under the CASA group, he taught me "Introduction to Java."
	He later mentored me during my honours thesis, which spun off a joint paper with him.
	I am currently mentoring one of his students in New Zealand.
}


\cvsect{Professional References}

\entrys%
{Ameya Palande}{Director}
{MesonLabs Ltd. | Vancouver, British Colombia, Canada}
{\texttt{ON REQUEST} 

	Software development lead on the Lynx Secure Hypervisor Project, I work under his supervision and guidance.
}

\entrys%
{Aaron G. Graham}{Research Assistant}
{University of New Brunswick, Fredericton, New Brunswick, Canada}
{\texttt{ON REQUEST}

	Responsible for managing day to day operations across projects in CASA, he was my superior on the Eclipse OMR project.
}

\entrys%
{Dr. Paul Cook}{Assistant Dean}
{University of New Brunswick | Fredericton, New Brunswick, Canada}
{\texttt{ON REQUEST}

	Responsible for undergraduate affairs, he was my superior during my work as an instructor.
}

\ifdefined\coverLetter{%

	\clearpage

	\cvsect{Statement of Purpose}

	\rmfamily
	\large
	% we should be double spaced
	\doublespacing%
	% justified for cleanliness
	\justifying%
	% reset the indent and paragraph skip
	\parskip 0ex plus 0.2ex minus 0.1ex%
	\parindent1.5em%
	\begin{quote}{80}
		\input{\coverLetter} \hfill\\

		I am an asset since I can easily mentor and learn remotely or on-site.
		I am a frank, loyal, and autonomous employee; I will take on many responsibilities as I strive to learn, share, and create.
		In applying to the position, I wish to increase my breadth of knowledge and get new opportunities.
		I am grateful that you took the time to read this and am looking forward to hearing from you.\\[6pt]
		\noindent Sincerely,\\
		\indent Jean-Philippe Legault
	\end{quote}

}\fi

\end{document}

