\input{src/documentClass}

\begin{document}

\newcommand{\toptext}{%
During my master's in Computer Science, I have gained expertise in language runtimes and FPGA development.
My broad interests allow me to use lateral thinking to solve complex problems.
I can efficiently visualize problems, design solutions, and communicate abstract ideas, allowing me to be an effective team member.
My experience in academia, working two years as a senior, and as a lead developer, has shaped me into an effective leader.
Working on both commercial and open-source projects has made me adaptable to new workflows.
}

\input{src/header}

\input{src/education}

\cvsect{Travel Grant}

\tightentry{2020}{International Symposium on FPGA}{Monterey, California, United-States}
\tightentry{2019}{Cascon}{Markham, Ontario, Canada}
\tightentry{2018}{Cascon}{Markham, Ontario, Canada}
\tightentry{2018}{Castle}{Markham, Ontario, Canada}
\tightentry{2018}{Splash}{Boston, Massachusetts, Canada}
\tightentry{2018}{CMC Microsystem TEXPO}{Toronto, Ontario, Canada}

\vspace*{\baselineskip}
\cvsect{Mentoring {\footnotesize(Unofficial Supervision)}}

\tightentry{2020 -- cur.}{Daniel Stokes}{Honours, B.CS., University of Waikato, New Zealand}
\tightentry{2020 -- cur.}{Eve MacDonald}{Work Term, B.EE, University of New Brunswick, Canada}
\tightentry{2020}{Shrey Vyas}{Work Term, M.CS, University of New Brunswick, Canada}
\tightentry{2019 -- 2020}{Mohammad Sohrabi}{Ph.D. CS, University of New Brunswick, Canada}
\tightentry{2019 -- cur.}{Seyed Alireza Damghani}{M.  CS, University of New Brunswick, Canada}
\tightentry{2019}{Michael Flawn}{Honours, B.CS., University of New Brunswick, Canada}
\tightentry{2019}{Alexandrea Demmings}{Work Term, B.SwE, University of New Brunswick, Canada}
\tightentry{2019}{Julie Brown}{Work Term, B.CEE, University of New Brunswick, Canada}
\tightentry{2018}{Nasrin Eshraghi Ivari}{Ph.D. CS University of New Brunswick, Canada}


\nocite{*}
\blfootnote{Presentors are \underline{underlined}}

\defbibheading{pip}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{In Proceeding Papers}\vspace*{-6pt}}
\printbibliography[heading=pip, keyword=inprogresspapers]

\defbibheading{pubp}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Published Papers}\vspace*{-6pt}}
\printbibliography[heading=pubp, keyword=publishedpapers]

\defbibheading{diss}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Dissertations}\vspace*{-6pt}}
\printbibliography[heading=diss, keyword=dissertations]

\defbibheading{talks}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Talks}\vspace*{-6pt}}
\printbibliography[heading=talks, keyword=talks]

\defbibheading{poster}{\vspace*{-6pt}\vspace*{\baselineskip}\cvsect{Conference Posters}\vspace*{-6pt}}
\printbibliography[heading=poster, keyword=poster]

\vspace*{-6pt}
\vspace*{\baselineskip}

\input{src/experience}

\input{src/knowledge}

\input{src/references}

\end{document}
