I have worked on both commercial and open-source tools.
My broad interests allow me to have an open mind about different topics and use lateral thinking to solve complex problems.
I have done my undergraduate and master's at the University of New Brunswick, and I am now looking for new opportunities.

I acquired three years of studies in Aerospace Engineering at a college, lending me a solid background in mission-critical systems.
During my studies, I have acquired strong understanding and abilities in mechanical engineering concepts such as CAD design, assembly, metallurgy, composite materials;
requirements and tolerances in aerospace are the smallest in the industry, given safety, performance, and cost are the primordial goals.
My first introduction to CAD tools quickly made me realize the potential and the drawbacks of the tools available; I changed vocation to computer science to learn to improve these.

My rapid growth from having no experience in software development when I started my bachelors (2015) is a testament to my desire and ability to learn and create.
During my undergraduate, I joined my studies with my passion for electronics. My undergraduate honour was on FPGA architecture development using the Odin II CAD tool---an FPGA computer-aided design tool synthesis tool.
I have continued to work on the project and am currently the lead developer; this has allowed me to learn to design, maintain, and administer projects.
I have contributed to numerous papers and mentored fellow researchers from Canada to New-Zealand.
The experience I have acquired working under IBM for my masters has allowed me to learn to develop features for large scale projects and collaborate with team members worldwide.
My experience with digital compilers (Verilog synthesis tool) and JIT compilers (JVM) give me a profound understanding of how compilers and high-level languages operate.

Outside of computer science, electronics has always been a passion; I have been ``modding'' gaming consoles ever since I learned to solder in elementary school.
I have professionally repaired household devices like power amplifiers, cellphones, televisions, computers, motherboards.
I have experience working with surface mount components and understand the challenges they pose.

I can be an asset since I can easily mentor and learn remotely and on-site, as shown by my experience.
I am frank, loyal, and autonomous; I will take on many responsibilities as I strive to learn, share, and create.
