\vspace*{6pt}

\cvsect{Experience}

\tightentry
{Jul. 2023 -- Sep. 2023}
{Staff Software Developer}
{Rivian Automotive LLC. -- \href{https://rivian.com/}{rivian.com} | CA, US}

\tightentry
{May 2022 -- Jul. 2023}
{Senior Software Developer}
{Rivian Automotive LLC. -- \href{https://rivian.com/}{rivian.com} | CA, US}

\entrys
{Apr. 2021 -- May 2022}
{Senior Software Developer}
{Rivian Automotive Canada, Inc -- \href{https://rivian.com/}{rivian.com} | BC, Canada}{
	Create services and middleware for Rivian's in-vehicle infotainment system which links drivers and passengers to their vehicle and the outside world.
	\begin{tightemize}
		\item Collaborate with Platform Software, HMI developers, System Design, and Test Engineers to realize a modern in-vehicle experience.
		\item Test the in-vehicle experience in the lab and in vehicles.
		\item Troubleshoot and resolve issues found on customers vehicle.
		\item Work with extensively Android AOSP and QNX Hypervisor at the platform and service level.
		\item Create a holistic logging solution for different ECU's, help improve in-house IPC solutions.
	\end{tightemize}
}

\entrys
{Nov. 2020 -- Apr. 2021}
{Software Developer}
{Meson Labs Ltd. -- \href{https://www.mesonlabs.ca/}{mesonlabs.ca} | Canada}{
	Improve a secure Pre-Boot Authentication image to chainload signed kernels and accessorize OPAL SED tools for PBA image using Bash.
	\begin{tightemize}
		\item Use Buildroot extensively to create embedded images.
		\item FPM to package applications.
		\item Built a framework to automate binaries/files installation/update/downgrade into an image using FPM and Makefiles.
		\item Review other developers' code.
		\item Patch drivers for Windows and Linux.
	\end{tightemize}
}

\entrys
{Sep. 2019 -- Nov. 2020}
{Lead Developer}
{Centre for Advance Studies Atlantic -- \href{https://www.unb.ca/research/casatlantic/}{unb.ca/research/casatlantic} | NB, Canada}{
	Maintain the Synthesis tool of the Verilog to Routing Project, Odin II and manage the Odin II project.
	\begin{tightemize}
		\item Architect design changes and new features for developers and myself to implement.
		\item Mentor new developers and carve a roadmap for them as well as manage and review their merge request.
		\item Improve the regression suite to catch bugs and regression in features.
        \item Devise unit test infrastructure to avoid introducing errors and improve our developers speed.
	\end{tightemize}
}

\entrys
{May 2019 -- Jul 2019}
{Instructor --- Systems Software Development}
{University of New Brunswick -- \href{https://www.unb.ca}{unb.ca} | NB, Canada}{
    Procedural program development and supporting tools, using the C language.
    Topics include implementation of data structures, memory management, compilation/linking, building, debugging, and version control.
}

% \entrys
% {Mar. 2019 - Apr. 2019}
% {Software Developer -- \textit{Contract}}
% {Butterfly Energy Systems -- \href{http://www.butterflyenergy.ca/home.php}{butterflyenergy.ca} | NB, Canada}{
% 	Responsible to track down a null pointer exception in a multithreaded C++ OOP codebase.
% 	It was traced back to a race condition because of an uncaught spurious wake of a thread; A class was deleted during the execution of one of its method.
% }

\ifdefined\academicCV {%
\entrys
{\normalsize
    Contracts\\
	\begin{tightemize}
		\timestamp{WI-2018}
		\timestamp{SM-2018}
		\timestamp{FA-2018}
	\end{tightemize}
}
{Teaching Assistant}
{University of New Brunswick | NB, Canada}
{
	\begin{tightemize}
		\item Computability and Formal Languages
		\item Professional Practices
		\item Professional Practices
	\end{tightemize}
}

\entrys
{\normalsize
    Contracts\\
	\begin{tightemize}
		\timestamp{FA-2018}
	\end{tightemize}
}
{Tutor}
{University of New Brunswick | NB, Canada}
{
	\begin{tightemize}
		\item Operating Systems I (CS3413) Rachelle Potter
	\end{tightemize}
}

}
\fi


% \entrys
% {2015 -- 2018}
% {Electronic and Software Technician}
% {Canada Electronic Parts Online Inc. | NB, Canada}{
% 	Repairing electronic devices, i.e. smartphones, televisions, computers.
% 	\begin{tightemize}
% 		\item Played a significant role in increasing sales and revenue by increasing outreach.
% 		\item Broadened the company's expertise in electronic repairs and introduced tooling and techniques to repair devices with surface mount components.
% 		\item Increased repairs success rate and revenue.
% 		\item Introduced software-based repairs and debugging (i.e. reflashing lost IMEI or CMOS)
% 		\item Introduced corrupted or defective hard drive data recovery.
% 	\end{tightemize}
% }


\vspace*{6pt}
\cvsect{Project Contributions}

\entrys
{2018 -- 2020}
{Eclipse OMR}
{\href{https://github.com/eclipse/omr}{github.com/eclipse/omr}}{
	Responsible for initiating the work on the basic implementation of an ARM64V8 specific OMR; This involved making the full suite of hardware operation in the ARM64V8 documentation (or AArch64) available to the JIT compiler.
	Weekly meetings were held on infrastructure design and implementation.
	The project was lead by the IBM Runtimes Team in Ottawa, and work was done conjointly with members of the IBM Japan team.
}

\entrys
{2017 -- 2020}
{Odin II}
{\href{https://github.com/verilog-to-routing/vtr-verilog-to-routing/graphs/contributors}{github.com/verilog-to-routing/vtr-verilog-to-routing}}{
	Maintain the Front-End Verilog Synthesis tool of the Verilog to Routing Project.
	\begin{tightemize}
		\item Managing other developers and review their merge requests.
		\item Fix Bugs and broken features.
		\item Build new features and improve the tool usability and documentation for both developers and users.
	\end{tightemize}
}
